\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual Multi-Loop Integrands

### 2023-09-22 notes/2loopNLSM.tex
conclusion

We concede building loop-level numerators from rational functions of the kinematics
is rather unnatural from the perspective of point-like quantum field
theories. After all, operators that produce rational functions are typically non-local in their construction. The archetypal example of non-local quantum operators are string vertex operators with $\alpha'$ corrections. These operators promote local tree-level amplitudes to stringy extended objects by integrating over disc integrals of the open string worldsheet:
\be
\mathcal{A}^{\text{YM}} \stackrel{\alpha'}{\longrightarrow} \mathcal{A}^{\text{OS}}\supset t_8 F^4 \int_0^1 dx \,\frac{ x^{\alpha' s_{12}}(1-x)^{\alpha' s_{23}}}{x(1-x)(s_{12}+s_{23})}
\ee
The resulting Veneziano factor of Gamma functions produces rational functions of kinematics, while preserving the color-dual structure color and kinematic factors \cite{Carrasco:2019yyn}. While introducing some type of worldsheet formulation of color-dual numerators might seem unjustified given the results of this work, our findings certainly suggest that we must do \textit{something} to relax the constraint of off-shell locality, and realize locality only in the limit of
\textit{on-shell} kinematics. This could be acheived by either modifying the kinetic term or potentially something new and more exotic. Below we provide some simple examples
at tree-level of what one might consider for implementing such a construction.

>>>>

We concede building loop-level numerators from rational functions of the kinematics
is rather unnatural from the perspective of point-like quantum field
theories. After all, operators that produce rational functions are typically non-local in their construction. The archetypal example of non-local quantum operators are string vertex operators with $\alpha'$ corrections. These operators promote local tree-level amplitudes to stringy extended objects by integrating over disc integrals of the open string worldsheet:
\be
\mathcal{A}^{\text{YM}} \stackrel{\alpha'}{\longrightarrow} \mathcal{A}^{\text{OS}}\supset t_8 F^4 \int_0^1 dx \,\frac{ x^{\alpha' s_{12}}(1-x)^{\alpha' s_{23}}}{x(1-x)(s_{12}+s_{23})}
\ee
The resulting Veneziano factor of Gamma functions produces rational functions of kinematics, while preserving the color-dual structure color and kinematic factors \cite{MafraBCJAmplString,Broedel:2013tta,Mafra:2016mcc,Carrasco:2019yyn}. While introducing some type of worldsheet formulation of color-dual numerators might seem unjustified given the results of this work, our findings certainly suggest that we must do \textit{something} to relax the constraint of off-shell locality, and realize locality only in the limit of
\textit{on-shell} kinematics. This could be acheived by either modifying the kinetic term or potentially something new and more exotic. Below we provide some simple examples
at tree-level of what one might consider for implementing such a construction.
